Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/results-devices.tex
sprinkled things to talk about inline
initial progress on results:devices

\subsubsection{Device}
Participants had unique VURs for scenarios only differing in device. Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2. The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Question &  Wearable VUR & Smartphone VUR \\
 \hline
 All & 58.79\% & 46.64\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.74\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\hline
\end{tabular}
\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

>>>>

%!TEX root = ../paper.tex

\subsubsection{Device}
{\color {red} intro to this section}

The five questions were:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Q1: How would you feel if an app on your <device> vibrated your phone without asking you first?
\item Q2: How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item Q3: How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item Q4: How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item Q5: How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
\end{enumerate}

Participants had unique VURs for scenarios only differing in device. Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones. The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}. {\color {red} talk about the standard deviation of the devices in general--was there more spread for the answers wrt smartphones, cubetastic, or were they kind of all the same?} However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2. The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. Too few instances of participants answering both versions of questions occurred (34 in total for all 5 questions) to perform a sound within-subjects analysis.

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Question &  Wearable VUR, $\sigma$ & Smartphone VUR, $\sigma$ \\
 \hline
 All & 58.79\%, \# & 46.64\%, \# \\
Q1 & 14.81\%,  \# &  6.13\%, \# \\
Q2 & 44.11\%, \# &  19.85\%, \# \\
Q3 & 87.09\%, \# &  58.44\%, \# \\
Q4 & 52.77\%, \# & 55.74\%, \# \\
Q5 & 86.49\%, \# &  91.82\%, \# \\ 
\hline
\end{tabular}
\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}
